A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-05-13 manuscript.Rmd
added comments to file path examples

To keep track of all changes on your local computer, you only need to use `git add` and `git commit` or `git commit -a` to add and commit at the same time. These commands need to be executed in the terminal, which you can access from within RStudio (`Shift + Alt + R`).  RStudio also offers a graphical user interface for Git. For most basic operations, this interface is convenient and sufficient.

![Git Pane in RStudio](Images/git-pane.png)

@@

```{r, eval=FALSE}
# BAD
iris <- read.csv("/home/aaron/reproducible-research/data/iris.csv")
# GOOD
iris <- read.csv("data/iris.csv")
# BETTER
iris <- read.csv(here("data", "iris.csv"))
```

>>>>

To keep track of all changes on your local computer, you only need to use `git add` and `git commit` or `git commit -a` to add and commit at the same time. These commands need to be executed in the terminal, which you can access from within RStudio (`Shift + Alt + R`).  RStudio also offers a graphical user interface for Git. For most basic operations, this interface is convenient and sufficient (see Figure \@ref{fig:gitpane}).

```{r gitpane, fig.cap="Git Pane providing easy access to basic functions in RStudio"}
knitr::include_graphics("Images/git-pane.png")
```

@@

```{r, eval=FALSE}
# BAD because of path that is specific to the computer
iris <- read.csv("/home/aaron/reproducible-research/data/iris.csv")
# GOOD because it is a relative path but slash depends on OS
iris <- read.csv("data/iris.csv")
# BETTER because truly compatible across OS
iris <- read.csv(here("data", "iris.csv"))
```
